Viscous Transport in Eroding Porous Media

### 2019-05-15 docs/transport/erosion_transport.tex
remove the repeat part of Fig.2 in transport paper
NM

\author[SH]{Shang-Huan Chiu}
\author[Nick]{M.~Nicholas J.~Moore}
\author[Bryan]{Bryan D.~Quaife}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Contributions}
\begin{itemize}
  \item Use novel near-singular Barycentric integration scheme for
    Stokes equation outlined in~\cite{bar-wu-vee2015}.
  \item Need to compute one additional derivative since we need the
    derivative of the velocity to find the vorticity and stress tensor
  \item Tracer trajectories at different time steps
  \item Compute the anomalous diffusion rate using similar techniques as
    the paper with Pietro~\cite{dea-qua-bir-jua2018}
  \item Need a novel way to do time stepping through the complex
    geometry
\end{itemize}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense_1}
\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense_101}\\

\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense_201}
\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense_301}
\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies with the fixed-pressure-drop condition. The color is the vorticity of fluid. The 4 snapshots are evenly spaced in time. In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $.}
\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense201}
\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense301}
\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies with the fixed-pressure-drop condition. The color is the vorticity of fluid. The 4 snapshots are evenly spaced in time. In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $. In the forth frame, bodies 4, 12, and 17 have vanished completely, and body 19 (the one without number on the right) has almost vanished because of eroding.}
\end{center}
\end{figure}
\subsection{20 nearly touching bodies}
{\color{red} 
By using Barycentric quadrature rule, 
we are able to capture the details in the fluid when wall and bodies or body and bodies 
are close to each other. 
The first nearly touching bodies case is 20 bodies in a Hagen-Poiseuille flow. 
The domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded corners. 
The velocity of flow from the left side of $\Omega$ is $v(x_1,x_2)=(1+x_2)(1-x_2)$. 
The number of discretization points $N_\iin$ on the bodies is 256 and the number 
of discretization points $N_\out$ on the outer boundary is 1024.

>>>>

\author[SH]{Shang-Huan Chiu}
\author[Nick]{M.~N.~J.~Moore}
\author[Bryan]{Bryan D.~Quaife}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Contributions}
\begin{itemize}
  \item Use novel near-singular Barycentric integration scheme for
    Stokes equation outlined in~\cite{bar-wu-vee2015}.
  \item Need to compute one additional derivative since we need the
    derivative of the velocity to find the vorticity and stress tensor
  \item Annealing algorithm to create initial body configurations of specified area fraction specified size distribution (NM can do the writing for this).
  \item Tracer trajectories at different time steps
  \item Compute the anomalous diffusion rate using similar techniques as
    the paper with Pietro~\cite{dea-qua-bir-jua2018}
  \item Need a novel way to do time stepping through the complex
    geometry
\end{itemize}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense1}
\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense101}\\

\includegraphics[width = 0.42 \textwidth]{./figs/20b_dense201}
\includegraphics[width = 0.507 \textwidth]{./figs/20b_dense301}
\caption{\label{fig:Eroding20vort} Erosion of 20 nearly touching bodies with the fixed-pressure-drop condition. The color is the vorticity of fluid. The 4 snapshots are evenly spaced in time. In this simulation, we use $N_\iin = 256$ discretization points on the body, $N_\out = 1024$ points on the outer boundary, a time-step of $\Dt=10^{-4}$, and smoothing parameters of $\eps= 15/256$ and $\sigma=10/256 $. In the forth frame, bodies 4, 12, and 17 have vanished completely, and body 19 (the one without number on the right) has almost vanished because of eroding.}
\end{center}
\end{figure}
\subsection{20 nearly touching bodies}
{\color{red} 
By using Barycentric quadrature rule, 
we are able to capture the details in the fluid when wall and bodies or body and bodies 
are close to each other. 
The first nearly touching bodies case is 20 bodies in a Hagen-Poiseuille flow. 
The domain $\Omega$ is a rectangle $[-3,3]\times[-1,1]$ with rounded corners. 
The velocity of flow from the left side of $\Omega$ is $v(x_1,x_2)=(1+x_2)(1-x_2)$. 
The number of discretization points $N_\iin$ on the bodies is 256 and the number 
of discretization points $N_\out$ on the outer boundary is 1024.
